% ==========================================================================
% daftar-pustaka.tex — master bibliografi, dibangkitkan oleh tools/make_biblio.py
% Jangan sunting manual; sunting references.bib lalu jalankan ulang.
% ==========================================================================
\chapter*{Daftar Pustaka}
\addcontentsline{toc}{chapter}{Daftar Pustaka}
\markboth{Daftar Pustaka}{}

\protect\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-alain2017probes}
Alain, Guillaume, and Yoshua Bengio. 2017. \emph{Understanding Intermediate Layers Using Linear Classifier Probes}. \url{https://arxiv.org/abs/1610.01644}.

\bibitem[\citeproctext]{ref-amershi2014power}
Amershi, Saleema, Maya Cakmak, W. Bradley Knox, and Todd Kulesza. 2014. {``Power to the People: The Role of Humans in Interactive Machine Learning.''} \emph{AI Magazine} 35 (4): 105--20.

\bibitem[\citeproctext]{ref-baevski2020wav2vec2}
Baevski, Alexei, Henry Zhou, Abdelrahman Mohamed, and Michael Auli. 2020. {``Wav2vec 2.0: A Framework for Self-Supervised Learning of Speech Representations.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}.

\bibitem[\citeproctext]{ref-baltrusaitis2019multimodal}
Baltrušaitis, Tadas, Chaitanya Ahuja, and Louis-Philippe Morency. 2019. {``Multimodal Machine Learning: A Survey and Taxonomy.''} \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence} 41 (2): 423--43.

\bibitem[\citeproctext]{ref-barocas2016disparate}
Barocas, Solon, and Andrew D. Selbst. 2016. {``Big Data's Disparate Impact.''} \emph{California Law Review} 104: 671--732.

\bibitem[\citeproctext]{ref-bergmeir2012cv}
Bergmeir, Christoph, and José M. Benítez. 2012. {``On the Use of Cross-Validation for Time Series Predictor Evaluation.''} \emph{Information Sciences} 191: 192--213.

\bibitem[\citeproctext]{ref-bommasani2021foundation}
{Bommasani, Rishi, Drew A. Hudson, Ehsan Adeli, et al.} 2021. \emph{On the Opportunities and Risks of Foundation Models}. \url{https://arxiv.org/abs/2108.07258}.

\bibitem[\citeproctext]{ref-boxcox1964}
Box, George E. P., and David R. Cox. 1964. {``An Analysis of Transformations.''} \emph{Journal of the Royal Statistical Society, Series B} 26 (2): 211--52.

\bibitem[\citeproctext]{ref-breck2017mltest}
Breck, Eric, Shanqing Cai, Eric Nielsen, Michael Salib, and D. Sculley. 2017. {``The {ML} Test Score: A Rubric for {ML} Production Readiness and Technical Debt Reduction.''} \emph{IEEE International Conference on Big Data}.

\bibitem[\citeproctext]{ref-breiman2001randomforests}
Breiman, Leo. 2001. {``Random Forests.''} \emph{Machine Learning} 45 (1): 5--32.

\bibitem[\citeproctext]{ref-vanbuuren2011mice}
Buuren, Stef van, and Karin Groothuis-Oudshoorn. 2011. {``{mice}: Multivariate Imputation by Chained Equations in {R}.''} \emph{Journal of Statistical Software} 45 (3): 1--67.

\bibitem[\citeproctext]{ref-cawley2010overfitting}
Cawley, Gavin C., and Nicola L. C. Talbot. 2010. {``On over-Fitting in Model Selection and Subsequent Selection Bias in Performance Evaluation.''} \emph{Journal of Machine Learning Research} 11: 2079--107.

\bibitem[\citeproctext]{ref-chen2020simclr}
Chen, Ting, Simon Kornblith, Mohammad Norouzi, and Geoffrey Hinton. 2020. {``A Simple Framework for Contrastive Learning of Visual Representations.''} \emph{Proceedings of the 37th International Conference on Machine Learning (ICML)}. \url{https://arxiv.org/abs/2002.05709}.

\bibitem[\citeproctext]{ref-dalal2005hog}
Dalal, Navneet, and Bill Triggs. 2005. {``Histograms of Oriented Gradients for Human Detection.''} \emph{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.

\bibitem[\citeproctext]{ref-devlin2019bert}
Devlin, Jacob, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova. 2019. {``{BERT}: Pre-Training of Deep Bidirectional Transformers for Language Understanding.''} \emph{Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics (NAACL-HLT)}.

\bibitem[\citeproctext]{ref-erickson2020autogluon}
Erickson, Nick, Jonas Mueller, Alexander Shirkov, et al. 2020. \emph{{AutoGluon-Tabular}: Robust and Accurate {AutoML} for Structured Data}. \url{https://arxiv.org/abs/2003.06505}.

\bibitem[\citeproctext]{ref-feurer2015autosklearn}
Feurer, Matthias, Aaron Klein, Katharina Eggensperger, Jost Springenberg, Manuel Blum, and Frank Hutter. 2015. {``Efficient and Robust Automated Machine Learning.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}.

\bibitem[\citeproctext]{ref-gama2014driftsurvey}
Gama, João, Indrė Žliobaitė, Albert Bifet, Mykola Pechenizkiy, and Abdelhamid Bouchachia. 2014. {``A Survey on Concept Drift Adaptation.''} \emph{ACM Computing Surveys} 46 (4): 1--37.

\bibitem[\citeproctext]{ref-grill2020byol}
{Grill, Jean-Bastien, Florian Strub, Florent Altché, Corentin Tallec, Pierre H. Richemond, et al.} 2020. {``Bootstrap Your Own Latent: A New Approach to Self-Supervised Learning.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}. \url{https://arxiv.org/abs/2006.07733}.

\bibitem[\citeproctext]{ref-groverleskovec2016}
Grover, Aditya, and Jure Leskovec. 2016. {``Node2vec: Scalable Feature Learning for Networks.''} \emph{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}. \url{https://arxiv.org/abs/1607.00653}.

\bibitem[\citeproctext]{ref-guyon2003selection}
Guyon, Isabelle, and André Elisseeff. 2003. {``An Introduction to Variable and Feature Selection.''} \emph{Journal of Machine Learning Research} 3: 1157--82.

\bibitem[\citeproctext]{ref-he2022mae}
He, Kaiming, Xinlei Chen, Saining Xie, Yanghao Li, Piotr Dollár, and Ross Girshick. 2022. {``Masked Autoencoders Are Scalable Vision Learners.''} \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}. \url{https://arxiv.org/abs/2111.06377}.

\bibitem[\citeproctext]{ref-he2016resnet}
He, Kaiming, Xiangyu Zhang, Shaoqing Ren, and Jian Sun. 2016. {``Deep Residual Learning for Image Recognition.''} \emph{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.

\bibitem[\citeproctext]{ref-hinton2006reducing}
Hinton, Geoffrey E., and Ruslan R. Salakhutdinov. 2006. {``Reducing the Dimensionality of Data with Neural Networks.''} \emph{Science} 313 (5786): 504--7.

\bibitem[\citeproctext]{ref-hollmann2023tabpfn}
Hollmann, Noah, Samuel Müller, Katharina Eggensperger, and Frank Hutter. 2023. {``{TabPFN}: A Transformer That Solves Small Tabular Classification Problems in a Second.''} \emph{International Conference on Learning Representations (ICLR)}.

\bibitem[\citeproctext]{ref-huber1981robust}
Huber, Peter J. 1981. \emph{Robust Statistics}. Wiley.

\bibitem[\citeproctext]{ref-hyndman2018forecasting}
Hyndman, Rob J., and George Athanasopoulos. 2018. \emph{Forecasting: Principles and Practice}. 2nd ed. OTexts.

\bibitem[\citeproctext]{ref-iglewiczhoaglin1993}
Iglewicz, Boris, and David C. Hoaglin. 1993. \emph{How to Detect and Handle Outliers}. ASQC Quality Press.

\bibitem[\citeproctext]{ref-kanter2015dfs}
Kanter, James Max, and Kalyan Veeramachaneni. 2015. {``Deep Feature Synthesis: Towards Automating Data Science Endeavors.''} \emph{IEEE International Conference on Data Science and Advanced Analytics (DSAA)}. \url{https://doi.org/10.1109/DSAA.2015.7344858}.

\bibitem[\citeproctext]{ref-kaufman2012leakage}
Kaufman, Shachar, Saharon Rosset, Claudia Perlich, and Ori Stitelman. 2012. {``Leakage in Data Mining: Formulation, Detection, and Avoidance.''} \emph{ACM Transactions on Knowledge Discovery from Data} 6 (4): 1--21. \url{https://doi.org/10.1145/2382577.2382579}.

\bibitem[\citeproctext]{ref-kipfwelling2017}
Kipf, Thomas N., and Max Welling. 2017. {``Semi-Supervised Classification with Graph Convolutional Networks.''} \emph{International Conference on Learning Representations (ICLR)}. \url{https://arxiv.org/abs/1609.02907}.

\bibitem[\citeproctext]{ref-kohavi1995cv}
Kohavi, Ron. 1995. {``A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection.''} \emph{Proceedings of the 14th International Joint Conference on Artificial Intelligence (IJCAI)}.

\bibitem[\citeproctext]{ref-leeseung1999nmf}
Lee, Daniel D., and H. Sebastian Seung. 1999. {``Learning the Parts of Objects by Non-Negative Matrix Factorization.''} \emph{Nature} 401: 788--91.

\bibitem[\citeproctext]{ref-lewis2020rag}
Lewis, Patrick, Ethan Perez, Aleksandra Piktus, et al. 2020. {``Retrieval-Augmented Generation for Knowledge-Intensive {NLP} Tasks.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}. \url{https://arxiv.org/abs/2005.11401}.

\bibitem[\citeproctext]{ref-littlerubin2019}
Little, Roderick J. A., and Donald B. Rubin. 2019. \emph{Statistical Analysis with Missing Data}. 3rd ed. Wiley.

\bibitem[\citeproctext]{ref-lundberg2017shap}
Lundberg, Scott M., and Su-In Lee. 2017. {``A Unified Approach to Interpreting Model Predictions.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}.

\bibitem[\citeproctext]{ref-vandermaaten2008tsne}
Maaten, Laurens van der, and Geoffrey Hinton. 2008. {``Visualizing Data Using t-{SNE}.''} \emph{Journal of Machine Learning Research} 9: 2579--605.

\bibitem[\citeproctext]{ref-mcinnes2018umap}
McInnes, Leland, John Healy, and James Melville. 2018. \emph{{UMAP}: Uniform Manifold Approximation and Projection for Dimension Reduction}. \url{https://arxiv.org/abs/1802.03426}.

\bibitem[\citeproctext]{ref-miccibarreca2001}
Micci-Barreca, Daniele. 2001. {``A Preprocessing Scheme for High-Cardinality Categorical Attributes in Classification and Prediction Problems.''} \emph{ACM SIGKDD Explorations Newsletter} 3 (1): 27--32.

\bibitem[\citeproctext]{ref-mikolov2013word2vec}
Mikolov, Tomas, Kai Chen, Greg Corrado, and Jeffrey Dean. 2013. \emph{Efficient Estimation of Word Representations in Vector Space}. \url{https://arxiv.org/abs/1301.3781}.

\bibitem[\citeproctext]{ref-ngiam2011multimodal}
Ngiam, Jiquan, Aditya Khosla, Mingyu Kim, Juhan Nam, Honglak Lee, and Andrew Y. Ng. 2011. {``Multimodal Deep Learning.''} \emph{Proceedings of the 28th International Conference on Machine Learning (ICML)}.

\bibitem[\citeproctext]{ref-pan2010transfer}
Pan, Sinno Jialin, and Qiang Yang. 2010. {``A Survey on Transfer Learning.''} \emph{IEEE Transactions on Knowledge and Data Engineering} 22 (10): 1345--59.

\bibitem[\citeproctext]{ref-pearson1901pca}
Pearson, Karl. 1901. {``On Lines and Planes of Closest Fit to Systems of Points in Space.''} \emph{Philosophical Magazine} 2 (11): 559--72.

\bibitem[\citeproctext]{ref-pedregosa2011sklearn}
Pedregosa, Fabian, Gaël Varoquaux, Alexandre Gramfort, et al. 2011. {``Scikit-Learn: Machine Learning in {P}ython.''} \emph{Journal of Machine Learning Research} 12: 2825--30.

\bibitem[\citeproctext]{ref-quionerocandela2009datasetshift}
Quiñonero-Candela, Joaquin, Masashi Sugiyama, Anton Schwaighofer, and Neil D. Lawrence. 2009. \emph{Dataset Shift in Machine Learning}. MIT Press.

\bibitem[\citeproctext]{ref-radford2021clip}
Radford, Alec, Jong Wook Kim, Chris Hallacy, et al. 2021. {``Learning Transferable Visual Models from Natural Language Supervision.''} \emph{Proceedings of the 38th International Conference on Machine Learning (ICML)}.

\bibitem[\citeproctext]{ref-reimers2019sbert}
Reimers, Nils, and Iryna Gurevych. 2019. {``Sentence-{BERT}: Sentence Embeddings Using Siamese {BERT}-Networks.''} \emph{Proceedings of the 2019 Conference on Empirical Methods in Natural Language Processing (EMNLP)}.

\bibitem[\citeproctext]{ref-ribeiro2016lime}
Ribeiro, Marco Tulio, Sameer Singh, and Carlos Guestrin. 2016. {``"Why Should {I} Trust You?": Explaining the Predictions of Any Classifier.''} \emph{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}.

\bibitem[\citeproctext]{ref-roberts2017spatialcv}
Roberts, David R., Volker Bahn, Simone Ciuti, et al. 2017. {``Cross-Validation Strategies for Data with Temporal, Spatial, Hierarchical, or Phylogenetic Structure.''} \emph{Ecography} 40 (8): 913--29. \url{https://doi.org/10.1111/ecog.02881}.

\bibitem[\citeproctext]{ref-saltonbuckley1988tfidf}
Salton, Gerard, and Christopher Buckley. 1988. {``Term-Weighting Approaches in Automatic Text Retrieval.''} \emph{Information Processing \& Management} 24 (5): 513--23.

\bibitem[\citeproctext]{ref-sculley2015debt}
Sculley, D., Gary Holt, Daniel Golovin, et al. 2015. {``Hidden Technical Debt in Machine Learning Systems.''} \emph{Advances in Neural Information Processing Systems (NeurIPS)}.

\bibitem[\citeproctext]{ref-tibshirani1996lasso}
Tibshirani, Robert. 1996. {``Regression Shrinkage and Selection via the Lasso.''} \emph{Journal of the Royal Statistical Society, Series B} 58 (1): 267--88.

\bibitem[\citeproctext]{ref-zheng2018feature}
Zheng, Alice, and Amanda Casari. 2018. \emph{Feature Engineering for Machine Learning: Principles and Techniques for Data Scientists}. O'Reilly Media.

\end{CSLReferences}
